|

### 2023-05-13 paper/00-main.Rmd
started on #10

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.pos = "p",
  cache = TRUE
)
library(here)
library(tidyverse)
```

@@

Big data bowl, Mike

>>>>

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
  # fig.pos = "p",
  # cache = TRUE
)
library(here)
library(tidyverse)
```

@@

We thank the organizers of the 2023 NFL Big Data Bowl for hosting the competition and providing access to the data.

### 2023-05-13 paper/01-introduction.Rmd
started on #10

Moreover, the sum of sacks, hits, and hurries is often defined as "pressures".
This is an improvement over sacks, but suffers from problems of subjectivity (e.g., whether there is an actual hurry or not).
Pro football focus (PFF) comes up with a metric called "pass-rush productivity" (PRP), which is a minor modification from the aforementioned pressures metric (see Table \ref{tab:metrics}).
In particular, PRP gives twice as much weight to a sack relative to hurries and hits, which is a slight improvement to pressures.
However, the choice of weights is ad-hoc and still only measures binary outcomes, similar to the shortcomings of previously discussed metrics.

>>>>

Moreover, the sum of sacks, hits, and hurries is often defined as (QB) pressures.
This is somewhat better than sacks, but suffers from problems of subjectivity (e.g., whether there is an actual hurry or not).
Pro football focus (PFF) comes up with a metric called "pass-rush productivity" (PRP), which is a minor modification from the aforementioned pressures metric (see Table \ref{tab:metrics}).
In particular, PRP gives twice as much weight to a sack relative to hurries and hits, which is a small upgrade to pressures.
However, the choice of weights is ad-hoc and still only measures binary outcomes, similar to the shortcomings of previously discussed metrics.

### 2023-05-13 paper/05-discussion.Rmd
started on #10

@@

Critique

Future work

rapm

>>>>

We have proposed STRAIN, a simple and interpretable statistic for evaluating pass-rushers, with higher STRAIN corresponds to greater pass-rushing ability. 
Compared to existing metrics, STRAIN measures pass-rush effectiveness for every play continuously over time, which is at a much more granular level than considering whether the play resulted in a sack or converting continuous data to a binary win/loss.

As for future directions, while we focus solely on pass-rushers in this paper, STRAIN can be easily extended to the assessment of pass-blockers as a unit. 
This can be accomplished by looking at quantities such as the total STRAIN or the maximum STRAIN per frame aggregated across the entire play.
It is also possible to apply STRAIN to assess individual offensive pass-blockers, provided that a method of matching blockers to rushers was developed.

@@

Critique/Limitations

Future work rapm
